---
title: "Assignment B-1"
author: "Ziwei Zhao"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

1. Go to canvas to get your invitation to create a GitHub repository for this project. You can find this in the description of Assignment B-1. Name your repo as you wish – keeping in mind that you’ll be using this repo for Assignment B-2, where you’ll be bundling your work from Assignment B-1 into an R package.
2. Make a new Rmd file containing all of your code. Be sure to use some dialogue between code chunks.

```{r}
#library(datateachr) # <- might contain the data you picked!
library(tidyverse)
library(datateachr)
library(palmerpenguins)
library(testthat)
library(dplyr)
library(gapminder)
library(digest)
#library(digest)
```

# Tidy Submission (15 points)

Follow these steps to submit your work. Be sure to familiarize yourself with the rubric for a tidy submission below, before doing these steps.

1. Make a README file for your repository. It should be a brief document letting a visitor know what’s in this repository (at a high level) and some key things they should know about how to use the files in the repository.
2. Tag a release in your GitHub repository corresponding to your submission before the deadline.
3. Grab the URL corresponding to your tagged release, and submit that to canvas.

## Rubric:

* The above steps were followed.
* Your work must be reproducible from beginning to end, error-free.
* Code should adopt a consistent and easy-to-read style – ideally, the tidyverse style, although we’re certainly not looking for strict adherence.
* You use proper English, spelling, and grammar, and write concisely. If there’s any uncertainty in determining a grade here, the UBC MDS writing rubric will be referred to.
* If there’s any further uncertainty in determining a grade for this tidy submission portion, the UBC MDS mechanics rubric will be referred to.

# Exercise 1: Make a Function (25 points)

In this exercise, you’ll be making a function and fortifying it. The function need not be complicated. The function need not be “serious”, but shouldn’t be nonsense.

## Function Ideas

* Did you repeat any code for a data analysis in STAT 545A? If so, consider making a function for this action.
* Consider bundling a specific `group_by() %>% summarise()` workflow.
* Write a wrapper around an existing function.
   * For example, perhaps accepting a narrower range of inputs (like not allowing logical vectors), or providing a different output.
   * A specific example: my `rqdist()` function is a wrapper around `quantreg::rq()`, narrowing its functionality.
   * It’s usually better to narrow a function’s focus than to broaden, so that a function doesn’t end up doing too much.
*   Make a function extracting parts of an `"lm"` object that you can’t easily access (`broom` aside), or measuring the “difference” between a linear and quadratic fit.
*   Make a special plot that you’d want to repeat when exploring your data.
*   ...

## Guidelines

* Your function should not rely on anything from your working environment.
* Your function should not rely on “magic numbers” – pre-selected numbers (or options) that appear inside the function that can’t be accessed by a user of the function.
   * For example, maybe `quantile(x, type = 1, ...)` appears in your function. The choice of 1 is arbitrary – unless you’re making a function like `quantile_type_1()`.
* Input should not take a rigid form. An example that’s too rigid is a data frame that’s expected to have special types of columns.
* The output is consistent – for example, always gives a list. An example of inconsistent output: `sapply(1:3, seq_len)` gives a list, and `sapply(1:3, sqrt)` gives an (atomic) vector.
* Your function includes appropriate arguments. (Do you handle NA’s appropriately? Are you using the ellipsis properly? etc.)


# Exercise 2: Document your Function (20 points)

In the same code chunk where you made your function, document the function using `roxygen2 tags`. Be sure to include:

1. Title.
2. Function description: In 1-2 brief sentences, describe what the function does.
3. Document each argument with the `@param` tag, making sure to justify why you named the parameter as you did.
* (Justification for naming is not often needed, but we want to hear your reasoning.)
4. What the function returns, using the `@return` tag.

```{r}
# Exercise 1 & Exercise 2

#' Count the data number of each group
#' @description `count_group_by` returns the number of the value choose_value in the column group_by_column of the data set dataset
#' @param dataset the data set that we choose to use
#' @param group_by_column the column that we choose to apply group_by function on
#' @param choose_value the value that we want to count
#' @return A 1 x 2 tibble with value "choose_value" in column "group_by_column" and the count number n of this value

count_group_by <- function(dataset, group_by_column, choose_value) {
  if (!is.character(group_by_column)) {
    stop("group_by_column must be a string.")
  }
  if (is.na(choose_value)) {
    stop("choose_value should not be NA.")
  }
  return(dataset %>% 
    drop_na(group_by_column) %>%
    group_by(.data[[group_by_column]]) %>%
    count() %>%
    filter(.data[[group_by_column]] == choose_value))
}
```

# Exercise 3: Include examples (15 points)

Demonstrate the usage of your function with a few examples. Use one or more new code chunks, describing what you’re doing.

Note: If you want to deliberately show an error, you can use `error = TRUE` in your code chunk option.

Here, we choose the `building_permits` dataset and test whether there are suitable variable in this dataset
```{r}
head(building_permits)
```
We can find that the variables `type_of_work` and `issue_date` might be a suitable column to use group_by function.
First, we want to know how many **New Building** in these buildings.

```{r}
count_group_by(building_permits, "type_of_work", "New Building")
```
Second, we want to know how many building's issue date is **2017-02-02**.

```{r}
count_group_by(building_permits, "issue_date", as.Date("2017-02-02", format = "%Y-%m-%d"))
```
Third, we want to know how many buildings project_value is **0**.

```{r}
count_group_by(building_permits, "project_value", 0)
```
Throw an error if choose_value is NA.
```{r, error = TRUE}
count_group_by(building_permits, "type_of_work", NA)
```

Throw an error if the column format is wrong.
```{r, error = TRUE}
count_group_by(building_permits, 33, "New Building")
```

# Exercise 4: Test the Function (25 points)

Running examples is a good way of checking by-eye whether your function is working as expected. But, having a formal “yes or no” check is useful when you move on to other parts of your analysis.

Write formal tests for your function. You should use at least three non-redundant uses of an `expect_()` function from the `testthat` package, and they should be contained in a `test_that()` function (or more than one). They should all pass.

Example of non-redundant inputs:

* Vector with no NA’s
* Vector that has NA’s
* Vector of a different type (if relevant)
* Vector of length 0, like `numeric(0)`.

Example of redundant inputs:

* Providing a different number (unless one of these numbers have some significance, like a limit point – just tell us if that’s the case)

First, we use the expect_equal() to test if the value is the same with the true value, then we use the expect_error() to test if inputting a wrong value throws an error
```{r}
test_that("Testing count_group_by function with dataset building_permits", {
  expect_equal(count_group_by(building_permits, "type_of_work", "New Building"), building_permits %>% drop_na(type_of_work) %>% group_by(type_of_work) %>% count() %>% filter(type_of_work == "New Building"))
  expect_equal(count_group_by(building_permits, "issue_date", as.Date("2017-02-04", format = "%Y-%m-%d")), building_permits %>% drop_na(issue_date) %>% group_by(issue_date) %>% count() %>% filter(issue_date == as.Date("2017-02-04", format = "%Y-%m-%d")))
  expect_equal(count_group_by(building_permits, "project_value", 0), building_permits %>% drop_na(project_value) %>% group_by(project_value) %>% count() %>% filter(project_value == 0))
  
  expect_error(count_group_by(building_permits, "address", NA), "choose_value should not be NA.")
  expect_error(count_group_by(building_permits, "permit_number", NA), "choose_value should not be NA.")
  expect_error(count_group_by(building_permits, 21, "Addition / Alteration"), "group_by_column must be a string.")
})
```

